---
title: "vignettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Req's objective is to paint a comprehensive and historical picture of the Québec economy. The package provides insight into past and current trends 

of the businesses created in Quebec by constructing a geographical representation of where and when each business exists (or existed), 

as well as details about the business (i.e., what industry the business is in, how many employees it has, etc.)

## Installation

You can install the development version of req like so:
#### J'aurai peut-être besoin de conseils sur ce qu'il faut mettre là... ####

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## How-To

### Step 1: Getting the business's industry code

A user needs to first know the corresponding industry code of a certain business

```{r, eval = FALSE}
Req_industry() # A list of all industries and their respective codes (from the Registraire des Entrprises) will be produced

Req_industry(industry="Boulangeries et pâtisseries") # A list of all businesses in the boulangerie et pâtisserie industry and their respective codes (from the Registraire des Entrprises) will be produced

Req_industry("Boulangeries et pâtisseries") # A list of all businesses in the boulangerie et pâtisserie industry and their respective codes (from the Registraire des Entrprises) will be produced

Req_industry("Boula") # A list of all businesses in an industry that contains the string "Boula" and their respective codes (from the Registraire des Entrprises) will be produced
```

### Step 2: Getting the business's number of employees code

Next, a user needs to know the possible ranges of the number of employees and their corresponding codes

```{r, eval = FALSE}
Req_employee() # A list of all possible ranges of number of employees and their respective codes (from the Registraire des Entrprises) will be produced
```


### Step 3: 
